The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-10-21 paper.tex
Minor formatting changes

\ex. \label{sonangle_formula} Formula: \textsc{SonAngle} = $arctan(V-C_1) - arctan(C_2-C_1)$

@@

\ex. \a. \textsc{SonAngle}(NT) =  $arctan(6-3) - arctan(1-3)$ = 2.35
     \b. \textsc{SonAngle}(TT) =  $arctan(6-1) - arctan(1-1)$ = 1.37
     \c. \textsc{SonAngle}(TN) =  $arctan(6-1) - arctan(3-1)$ = 0.27

@@

\vspace{-3em}
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/TF/} & {\sc Id(SA)}$<$2.0 & {\sc Id(SA)}$<$1.5 & {\sc *CompCoda} & {\sc Id(SA)}$<$1.0 & {\sc Id(SA)}$<$0.5 \\[0.5ex]
\hline \hline a. & & TF & & & $\ast$! & \cellcolor{lightgray} & \cellcolor{lightgray} \\
\hline b. & \ding{43} & T\textipa{@}F & 0.59 & 0.59 & & \cellcolor{lightgray}0.59 & \cellcolor{lightgray}0.59 $\ast$ \\
\hline \end{tabular}} %\renewcommand*\arraystretch{1} \end{center}

\bigskip
%\begin{center} \renewcommand*\arraystretch{1.2}
%\scalebox{1}[1]
{\begin{tabular}[t]{|rrl||c|c|c|c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/FT/} & {\sc Id(SA)}$<$2.5 & {\sc Id(SA)}$<$1.5 & {\sc *CompCoda} & {\sc Id(SA)}$<$1.0 & {\sc Id(SA)}$<$0.5 \\[0.5ex]
\hline \hline c. & \ding{43}& FT & & & \cellcolor{lightgray} $\ast$ & \cellcolor{lightgray} & \cellcolor{lightgray} \\
\hline d. &  & F\textipa{@}T & 2.11 & 2.11 $\ast$! & \cellcolor{lightgray} & \cellcolor{lightgray} 2.11 $\ast$ & \cellcolor{lightgray}2.11 $\ast$ \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
\vspace{0.5em}

@@

\ex. {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ $\mathcal{M}$
     \a. Scenario 1: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}), {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$<$n \\
         Since neither violates {\sc Ident(Son$\measuredangle$)}$<$n, $\mathcal{M}$ determines output.
\vspace{-0.5em}
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n & $\mathcal{M}$ \\[0.5ex]
\hline \hline a. & \ding{43} & C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $<$n & \\
\hline b. & & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $<$n & $\ast$! \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
\vspace{0.5em}
      \b. Scenario 2: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2})$>$n, {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$<$n \\
          C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} harmonically bound by C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} candidate.
\vspace{-0.5em}
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n &$ \mathcal{M}$  \\[0.5ex]
\hline \hline c. & \ding{43} &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3}  & $<$n & \cellcolor{lightgray} \\
\hline d. & & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $>$n $\ast$! & \cellcolor{lightgray}$\ast$ \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
\vspace{0.5em} \newpage
     \c. Scenario 3: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2})$<$n, {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$>$n \\
         {\sc Ident(Son$\measuredangle$)}$<$n determines output, overruling $\mathcal{M}$.
\vspace{-0.5em}
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n &$ \mathcal{M}$  \\[0.5ex]
\hline \hline e. & &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $>$n $\ast$!  & \cellcolor{lightgray} \\
\hline f. & \ding{43} & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3}& $<$n  & \cellcolor{lightgray}$\ast$ \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
\vspace{0.5em}
     \d. Scenario 4: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}), {\sc SonAngle}(C\textsubscript{2}C\textsubscript{3}) $>$ n \\
         Since both candidates violate {\sc Ident(Son$\measuredangle$)}$<$n, $\mathcal{M}$ determines output.
\vspace{-0.5em}
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n &$ \mathcal{M}$  \\[0.5ex]
\hline \hline g. & &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $>$n $\ast$  & \\
\hline h. & \ding{43} & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $>$n $\ast$ & $\ast$! \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
\vspace{0.5em}

@@

\ex. Scenario: {\sc SonAngle}(C\textsubscript{2}C\textsubscript{3}) $>$ {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}) $>$ n \\

@@

	\node (TR) at (0.124354994547*8, 1) {TR};
	\node (Tb) at (0.183110817262*8, 0.5) {T\textipa{B}};
	\node (FR) at (0.218668945874*8, 1) {FR};
	\node (TN) at (0.266252049151*8, 1.5) {TN};
	\node (Fb) at (0.343023940421*8, 1) {F\textipa{B}};
	\node (NR) at (0.463647609001*8, 1) {NR};
	\node (FN) at (0.540419500271*8, 0.5) {FN};
	\node (TF) at (0.588002603548*8, 1) {TF};
	\node (bR) at (0.726642340682*8, 0.5) {\textipa{B}R};
	\node (Nb) at (0.785398163397*8, 1) {N\textipa{B}};
	\node (RR) at (1.10714871779*8, 1) {RR};
%	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
	\node (NN) at (1.2490457724*8, 1) {NN};
	\node (FF) at (1.32581766367*8, 1.5) {FF};
	\node (TT) at (1.37340076695*8, 1) {TT};
	\node (Rb) at (1.57079632679*8, 1) {R\textipa{B}};
	\node (bN) at (1.65393755868*8, 0.5) {\textipa{B}N};
	\node (RN) at (1.89254688119*8, 1) {RN};
	\node (NF) at (2.0344439358*8, 1) {NF};
%	\node (GF) at (2.0344439358*8, 1.5) {GF};
	\node (FT) at (2.11121582707*8, 0.5) {FT};
	\node (bF) at (2.17308367293*8, 1) {\textipa{B}F};
	\node (RF) at (2.21429743559*8, 1.5) {RF};
	\node (RT) at (2.35619449019*8, 1) {RT};
	\node (NT) at (2.35619449019*8, 0.5) {NT};
	\node (bT) at (2.38057989937*8, 1.5) {\textipa{B}T};
  \node (rising) at (0.3*8,2.3) {\underline{Rising sonority}};
  \node (level) at (1.2*8,2.3) {\underline{Level sonority}};
  \node (falling) at (2.2*8,2.3) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,0) {};
  \node (axisend)   at (2.7*8,0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
  \node (0pointlabel) at (0.0,-0.5) {0};
  \node (1pointlabel) at (1.0*8,-0.5) {1};
  \node (2pointlabel) at (2.0*8,-0.5) {2};
  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
  % dividing line
  \node (dividinglinestart) at (1.5 * 8,2) {};
  \node (dividinglineend)   at (1.5 * 8,-0.3) {};
  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
  \node (dividingpointlabel) at (1.5*8, -0.5) {1.5};
\end{tikzpicture}
}

@@

	\node (TR) at (0.124354994547*8, 1) {TR};
	\node (Tb) at (0.183110817262*8, 0.5) {T\textipa{B}};
	\node (FR) at (0.218668945874*8, 1) {FR};
	\node (TN) at (0.266252049151*8, 1.5) {TN};
	\node (Fb) at (0.343023940421*8, 1) {F\textipa{B}};
	\node (NR) at (0.463647609001*8, 1) {NR};
	\node (FN) at (0.540419500271*8, 0.5) {FN};
	\node (TF) at (0.588002603548*8, 1) {TF};
	\node (bR) at (0.726642340682*8, 0.5) {\textipa{B}R};
	\node (Nb) at (0.785398163397*8, 1) {N\textipa{B}};
	\node (RR) at (1.10714871779*8, 1) {RR};
%	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
	\node (NN) at (1.2490457724*8, 1) {NN};
	\node (FF) at (1.32581766367*8, 1.5) {FF};
	\node (TT) at (1.37340076695*8, 1) {TT};
	\node (Rb) at (1.57079632679*8, 1) {R\textipa{B}};
	\node (bN) at (1.65393755868*8, 0.5) {\textipa{B}N};
	\node (RN) at (1.84*8, 1) {RN}; %1.89254688119
	\node (NF) at (2.0344439358*8, 1) {NF};
%	\node (GF) at (2.0344439358*8, 1.5) {GF};
	\node (FT) at (2.11121582707*8, 0.5) {FT};
	\node (bF) at (2.17308367293*8, 1) {\textipa{B}F};
	\node (RF) at (2.21429743559*8, 1.5) {RF};
	\node (RT) at (2.35619449019*8, 1) {RT};
	\node (NT) at (2.35619449019*8, 0.5) {NT};
	\node (bT) at (2.38057989937*8, 1.5) {\textipa{B}T};
  \node (rising) at (0.3*8,2.3) {\underline{Rising sonority}};
  \node (level) at (1.2*8,2.3) {\underline{Level sonority}};
  \node (falling) at (2.2*8,2.3) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,0) {};
  \node (axisend)   at (2.7*8,0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
  \node (0pointlabel) at (0.0,-0.5) {0};
  \node (1pointlabel) at (1.0*8,-0.5) {1};
  \node (2pointlabel) at (2.0*8,-0.5) {2};
  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
  % dividing line
  \node (dividinglinestart) at (1.9 * 8,2) {};
  \node (dividinglineend)   at (1.9 * 8,-0.3) {};
  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
  \node (dividingpointlabel) at (1.9*8, -0.5) {1.9};
  \path [line,dotted] (1.5 * 8,1.8) -- (1.91 * 8, 1.8);
\end{tikzpicture}
}

@@

\noindent {\bf Remark on conflation.} Notice that all distinctions among the set of rising and level sonority clusters on the one hand, and the distinctions among the set of falling sonority clusters, are conflated. For instance, consider the cluster /mst/. {\sc SonAngle}(m,s), at 2.03, is smaller than {\sc SonAngle}(s,t), at 2.11, yet epenthesis occurs on the right, creating the larger {\sc Sonority Angle}. This is because the distinction between {\sc Sonority Angles} of 2.03 and 2.11 is irrelevant under the given  constraint ranking, since both 2.03 and 2.11 violate the relevant faithfulness constraint {\sc Ident(Son$\measuredangle$)}$<$1.5. This is possible because I have adopted the position that the {\sc Ident(Son$\measuredangle$)}$<$n constraints can be freely ranked, following \cite{de.lacy.2004}.

@@

Given the general form of the ranking {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ {\sc Align-Left} $\gg$ {\sc Anchor-Left Root}, the expected behaviour of four-consonant clusters is as follows: all /CCCC/ clusters surface as [CC\textipa{1}CC], except when {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) exceeds n and {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) and {\sc SonAngle}(C\textsubscript{3},C\textsubscript{4}) are both smaller than n. Illustrative tableaux are shown below for n=1.5:

@@

Given the general form of the ranking {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ {\sc Anchor-Left Root} $\gg$ {\sc Align-Left}, the default behaviour is to epenthesise as [C\textipa{1}CC\textipa{1}C]. This preference is overridden when at least one of {\sc SonAngle}(C\textsubscript{1},C\textsubscript{2}) and {\sc SonAngle}(C\textsubscript{3},C\textsubscript{4}) are greater than n and {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3}) is less than n.

@@

The case studies here constitute insufficient data to conclude if any of these interpretations is correct. It is worth noting, however, that alternative approaches such as {\sc Sonority Rise} do not face this issue, as computing the gradients of the underlying contour /C\textsubscript{1}C\textsubscript{2}/ and the surface contour [C\textsubscript{1}V] does not depend on the two C\textsubscript{1}'s being the same.

@@

\ex. Intensity data for English males (in dB) \citep[Table 5.13]{parker.2002}\footnote{The intensity values measured for the three vowel classes are reversed from what one would expect according to phonological sonority \citep[214]{parker.2002}}, but overall this shows a good correlation with scales of phonological sonority. The distinction between some of these classes is not significant, including between the high and mid vowels.

@@

  \node (rising) at (0.3*8,3) {\underline{Rising sonority}};
  \node (level) at (1.5*8,3) {\underline{Level sonority}};
  \node (falling) at (2.2*8,3) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,0) {};
  \node (axisend)   at (3.2*8,0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
  \node (0pointlabel) at (0.0,-0.5) {0};
  \node (1pointlabel) at (1.0*8,-0.5) {1};
  \node (2pointlabel) at (2.0*8,-0.5) {2};
  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
\end{tikzpicture}
}

@@

\bibliographystyle{apalike}
\bibliography{sonangle}

>>>>

\ex. \label{sonangle_formula} Formula: {\sc Son$\measuredangle$} = $arctan(V-C_1) - arctan(C_2-C_1)$

@@

\ex. \a. {\sc Son$\measuredangle$}(NT) =  $arctan(6-3) - arctan(1-3)$ = 2.35
     \b. {\sc Son$\measuredangle$}(TT) =  $arctan(6-1) - arctan(1-1)$ = 1.37
     \c. {\sc Son$\measuredangle$}(TN) =  $arctan(6-1) - arctan(3-1)$ = 0.27

@@

\vspace{-2em}
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|c|c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/TF/} & {\sc Id(S$\measuredangle$)}$<$2.0 & {\sc Id(S$\measuredangle$)}$<$1.5 & {\sc *CompCoda} & {\sc Id(S$\measuredangle$)}$<$1.0 & {\sc Id(S$\measuredangle$)}$<$0.5 \\[0.5ex]
\hline \hline a. & & TF & & & $\ast$! & \cellcolor{lightgray} & \cellcolor{lightgray} \\
\hline b. & \ding{43} & T\textipa{@}F & 0.59 & 0.59 & & \cellcolor{lightgray}0.59 & \cellcolor{lightgray}0.59 $\ast$ \\
\hline \end{tabular}} %\renewcommand*\arraystretch{1} \end{center}

\bigskip
%\begin{center} \renewcommand*\arraystretch{1.2}
%\scalebox{1}[1]
{\begin{tabular}[t]{|rrl||c|c|c|c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/FT/} & {\sc Id(S$\measuredangle$)}$<$2.5 & {\sc Id(S$\measuredangle$)}$<$1.5 & {\sc *CompCoda} & {\sc Id(S$\measuredangle$)}$<$1.0 & {\sc Id(S$\measuredangle$)}$<$0.5 \\[0.5ex]
\hline \hline c. & \ding{43}& FT & & & \cellcolor{lightgray} $\ast$ & \cellcolor{lightgray} & \cellcolor{lightgray} \\
\hline d. &  & F\textipa{@}T & 2.11 & 2.11 $\ast$! & \cellcolor{lightgray} & \cellcolor{lightgray} 2.11 $\ast$ & \cellcolor{lightgray}2.11 $\ast$ \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
\vspace{0.5em}

@@

\ex. {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ $\mathcal{M}$
     \a. Scenario 1: {\sc Son$\measuredangle$}(C\textsubscript{1}C\textsubscript{2}), {\sc Son$\measuredangle$}(C\textsubscript{2},C\textsubscript{3})$<$n \\
         Since neither violates {\sc Ident(Son$\measuredangle$)}$<$n, $\mathcal{M}$ determines output.
\vspace{-0.5em}
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n & $\mathcal{M}$ \\[0.5ex]
\hline \hline a. & \ding{43} & C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $<$n & \\
\hline b. & & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $<$n & $\ast$! \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
\vspace{0.5em}
      \b. Scenario 2: {\sc Son$\measuredangle$}(C\textsubscript{1}C\textsubscript{2})$>$n, {\sc Son$\measuredangle$}(C\textsubscript{2},C\textsubscript{3})$<$n \\
          C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} harmonically bound by C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} candidate.
\vspace{-0.5em}
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n &$ \mathcal{M}$  \\[0.5ex]
\hline \hline c. & \ding{43} &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3}  & $<$n & \cellcolor{lightgray} \\
\hline d. & & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $>$n $\ast$! & \cellcolor{lightgray}$\ast$ \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
\vspace{0.5em} \newpage
     \c. Scenario 3: {\sc Son$\measuredangle$}(C\textsubscript{1}C\textsubscript{2})$<$n, {\sc Son$\measuredangle$}(C\textsubscript{2},C\textsubscript{3})$>$n \\
         {\sc Ident(Son$\measuredangle$)}$<$n determines output, overruling $\mathcal{M}$.
\vspace{-0.5em}
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n &$ \mathcal{M}$  \\[0.5ex]
\hline \hline e. & &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $>$n $\ast$!  & \cellcolor{lightgray} \\
\hline f. & \ding{43} & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3}& $<$n  & \cellcolor{lightgray}$\ast$ \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
\vspace{0.5em}
     \d. Scenario 4: {\sc Son$\measuredangle$}(C\textsubscript{1}C\textsubscript{2}), {\sc Son$\measuredangle$}(C\textsubscript{2}C\textsubscript{3}) $>$ n \\
         Since both candidates violate {\sc Ident(Son$\measuredangle$)}$<$n, $\mathcal{M}$ determines output.
\vspace{-0.5em}
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n &$ \mathcal{M}$  \\[0.5ex]
\hline \hline g. & &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $>$n $\ast$  & \\
\hline h. & \ding{43} & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $>$n $\ast$ & $\ast$! \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
\vspace{0.5em}

@@

\ex. Scenario: {\sc Son$\measuredangle$}(C\textsubscript{2}C\textsubscript{3}) $>$ {\sc Son$\measuredangle$}(C\textsubscript{1}C\textsubscript{2}) $>$ n \\

@@

	\node (TR) at (0.124354994547*8, 1) {TR};
	\node (Tb) at (0.183110817262*8, 0.5) {T\textipa{B}};
	\node (FR) at (0.218668945874*8, 1) {FR};
	\node (TN) at (0.266252049151*8, 1.5) {TN};
	\node (Fb) at (0.343023940421*8, 1) {F\textipa{B}};
	\node (NR) at (0.463647609001*8, 1) {NR};
	\node (FN) at (0.540419500271*8, 0.5) {FN};
	\node (TF) at (0.588002603548*8, 1) {TF};
	\node (bR) at (0.726642340682*8, 0.5) {\textipa{B}R};
	\node (Nb) at (0.785398163397*8, 1) {N\textipa{B}};
	\node (RR) at (1.10714871779*8, 1) {RR};
%	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
	\node (NN) at (1.2490457724*8, 1) {NN};
	\node (FF) at (1.32581766367*8, 1.5) {FF};
	\node (TT) at (1.37340076695*8, 1) {TT};
	\node (Rb) at (1.57079632679*8, 1) {R\textipa{B}};
	\node (bN) at (1.65393755868*8, 0.5) {\textipa{B}N};
	\node (RN) at (1.89254688119*8, 1) {RN};
	\node (NF) at (2.0344439358*8, 1) {NF};
%	\node (GF) at (2.0344439358*8, 1.5) {GF};
	\node (FT) at (2.11121582707*8, 0.5) {FT};
	\node (bF) at (2.17308367293*8, 1) {\textipa{B}F};
	\node (RF) at (2.21429743559*8, 1.5) {RF};
	\node (RT) at (2.35619449019*8, 1) {RT};
	\node (NT) at (2.35619449019*8, 0.5) {NT};
	\node (bT) at (2.38057989937*8, 1.5) {\textipa{B}T};
  \node (rising) at (0.3*8,2.3) {\underline{Rising sonority}};
  \node (level) at (1.2*8,2.3) {\underline{Level sonority}};
  \node (falling) at (2.2*8,2.3) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,0) {};
  \node (axisend)   at (2.7*8,0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
  \node (0pointlabel) at (0.0,-0.5) {0};
  \node (1pointlabel) at (1.0*8,-0.5) {1};
  \node (2pointlabel) at (2.0*8,-0.5) {2};
  \node (xaxislabel) at (2.7*8,-0.5) {{\sc Son$\measuredangle$}};
  % dividing line
  \node (dividinglinestart) at (1.5 * 8,2) {};
  \node (dividinglineend)   at (1.5 * 8,-0.3) {};
  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
  \node (dividingpointlabel) at (1.5*8, -0.5) {1.5};
\end{tikzpicture}
}

@@

	\node (TR) at (0.124354994547*8, 1) {TR};
	\node (Tb) at (0.183110817262*8, 0.5) {T\textipa{B}};
	\node (FR) at (0.218668945874*8, 1) {FR};
	\node (TN) at (0.266252049151*8, 1.5) {TN};
	\node (Fb) at (0.343023940421*8, 1) {F\textipa{B}};
	\node (NR) at (0.463647609001*8, 1) {NR};
	\node (FN) at (0.540419500271*8, 0.5) {FN};
	\node (TF) at (0.588002603548*8, 1) {TF};
	\node (bR) at (0.726642340682*8, 0.5) {\textipa{B}R};
	\node (Nb) at (0.785398163397*8, 1) {N\textipa{B}};
	\node (RR) at (1.10714871779*8, 1) {RR};
%	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
	\node (NN) at (1.2490457724*8, 1) {NN};
	\node (FF) at (1.32581766367*8, 1.5) {FF};
	\node (TT) at (1.37340076695*8, 1) {TT};
	\node (Rb) at (1.57079632679*8, 1) {R\textipa{B}};
	\node (bN) at (1.65393755868*8, 0.5) {\textipa{B}N};
	\node (RN) at (1.84*8, 1) {RN}; %1.89254688119
	\node (NF) at (2.0344439358*8, 1) {NF};
%	\node (GF) at (2.0344439358*8, 1.5) {GF};
	\node (FT) at (2.11121582707*8, 0.5) {FT};
	\node (bF) at (2.17308367293*8, 1) {\textipa{B}F};
	\node (RF) at (2.21429743559*8, 1.5) {RF};
	\node (RT) at (2.35619449019*8, 1) {RT};
	\node (NT) at (2.35619449019*8, 0.5) {NT};
	\node (bT) at (2.38057989937*8, 1.5) {\textipa{B}T};
  \node (rising) at (0.3*8,2.3) {\underline{Rising sonority}};
  \node (level) at (1.2*8,2.3) {\underline{Level sonority}};
  \node (falling) at (2.2*8,2.3) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,0) {};
  \node (axisend)   at (2.7*8,0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
  \node (0pointlabel) at (0.0,-0.5) {0};
  \node (1pointlabel) at (1.0*8,-0.5) {1};
  \node (2pointlabel) at (2.0*8,-0.5) {2};
  \node (xaxislabel) at (2.7*8,-0.5) {{\sc Son$\measuredangle$}};
  % dividing line
  \node (dividinglinestart) at (1.9 * 8,2) {};
  \node (dividinglineend)   at (1.9 * 8,-0.3) {};
  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
  \node (dividingpointlabel) at (1.9*8, -0.5) {1.9};
  \path [line,dotted] (1.5 * 8,1.8) -- (1.91 * 8, 1.8);
\end{tikzpicture}
}

@@

\noindent {\bf Remark on conflation.} Notice that all distinctions among the set of rising and level sonority clusters on the one hand, and the distinctions among the set of falling sonority clusters, are conflated. For instance, consider the cluster /mst/. {\sc Son$\measuredangle$}(m,s), at 2.03, is smaller than {\sc Son$\measuredangle$}(s,t), at 2.11, yet epenthesis occurs on the right, creating the larger {\sc Sonority Angle}. This is because the distinction between {\sc Sonority Angles} of 2.03 and 2.11 is irrelevant under the given  constraint ranking, since both 2.03 and 2.11 violate the relevant faithfulness constraint {\sc Ident(Son$\measuredangle$)}$<$1.5. This is possible because I have adopted the position that the {\sc Ident(Son$\measuredangle$)}$<$n constraints can be freely ranked, following \cite{de.lacy.2004}.

@@

Given the general form of the ranking {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ {\sc Align-Left} $\gg$ {\sc Anchor-Left Root}, the expected behaviour of four-consonant clusters is as follows: all /CCCC/ clusters surface as [CC\textipa{1}CC], except when {\sc Son$\measuredangle$}(C\textsubscript{2},C\textsubscript{3}) exceeds n and {\sc Son$\measuredangle$}(C\textsubscript{1},C\textsubscript{2}) and {\sc Son$\measuredangle$}(C\textsubscript{3},C\textsubscript{4}) are both smaller than n. Illustrative tableaux are shown below for n=1.5:

@@

Given the general form of the ranking {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ {\sc Anchor-Left Root} $\gg$ {\sc Align-Left}, the default behaviour is to epenthesise as [C\textipa{1}CC\textipa{1}C]. This preference is overridden when at least one of {\sc Son$\measuredangle$}(C\textsubscript{1},C\textsubscript{2}) and {\sc Son$\measuredangle$}(C\textsubscript{3},C\textsubscript{4}) are greater than n and {\sc Son$\measuredangle$}(C\textsubscript{2},C\textsubscript{3}) is less than n.

@@

The two case studies examined above present insufficient data to conclude if any of these interpretations is correct. It is worth noting, however, that alternative approaches such as {\sc Sonority Rise} do not face this issue, as computing the gradients of the underlying contour /C\textsubscript{1}C\textsubscript{2}/ and the surface contour [C\textsubscript{1}V] does not depend on the two C\textsubscript{1}'s being the same.

@@

\ex. Intensity data for English males (in dB) \citep[Table 5.13]{parker.2002}\footnote{The intensity values measured for the three vowel classes are reversed from what one would expect according to phonological sonority \citep[214]{parker.2002}, but overall this shows a good correlation with scales of phonological sonority. The distinction between some of these classes is not significant, including between the high and mid vowels.}

@@

  \node (rising) at (0.3*8,3) {\underline{Rising sonority}};
  \node (level) at (1.5*8,3) {\underline{Level sonority}};
  \node (falling) at (2.2*8,3) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,0) {};
  \node (axisend)   at (3.2*8,0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
  \node (0pointlabel) at (0.0,-0.5) {0};
  \node (1pointlabel) at (1.0*8,-0.5) {1};
  \node (2pointlabel) at (2.0*8,-0.5) {2};
  \node (xaxislabel) at (2.7*8,-0.5) {{\sc Son$\measuredangle$}};
\end{tikzpicture}
}

@@

\bibliographystyle{unified}
\bibliography{sonangle}
